Dark Control:\\ A Unified Account of Default Mode Function\\ by Markov Decision Processes

### 2017-09-18 paper/paper.tex
update Venn figure caption

Evidence form computional modeling in human behavior \citep{kording2004bayesian} and cell recording experiments in ferrets \citep{fiser2004small} suggest that
the human brain is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
The present paper proposes a
process model that satisfies this contention.
We also contribute to the discussion of DMN function
by providing some of the first empirical evidence that
morphological variability in DMN regions
is linked to the reward circuitry (Fig. 2).
Finally, we detail how our process model relates
to previous accounts of DMN function and
we derive explicit hypotheses to be tested in future neuroscience
experiments (Box 1).

@@

\begin{figure}[!h]
  \includegraphics[width=1\linewidth]{VennDiagram-2017-09-08.pdf}
  \caption{\textbf{Where does Markov Decision Process fit in the theoretical landscape?}
  This Venn diagram summarizes the relationship between four existing accounts of DMN: in blue colors, the Free Energy Principle \& Predictive Coding, more related to the ”How” DMN works, and in yellow, the Sentinel \& the Semantic hypotheses, more related to "What" DMN does. Our account of DMN by Markov Decision Process is at the intersection of those accounts and thus corresponds to a "Process model" meaning a model of both "How" and "What" a process occur.
  % ; here the mental processes and how it relate to observed behavior. For each account, 4 icons describe the core concepts of Time horizon, Neural plasticity, Hierarchy, and Behavioral goal. The "Time horizon" should be understood as a weighting of the expected future outcomes shorter to longer terms into present decision making. Then, "online monitoring" of the environment means detecting and processing salient cues in the sensory environment. The "Predictive Coding" is understood here as the joint minimization of feedforward prediction error and feedback modulation to optimize neural processing; there is thus no notion of an agent with behavioral goal.
  }
  \label{fig:VennDiagram}
\end{figure}

>>>>

Evidence from computional modeling of human behavior \citep{kording2004bayesian} and cell recording experiments in ferrets \citep{fiser2004small} suggest that
the human brain is largely dedicated to
``the development and maintenance of [a]
probabilistic model of anticipated events''
\citep{raichle2005intrinsic}.
The present paper proposes a
process model that satisfies this contention.
We also contribute to the discussion of DMN function
by providing some of the first empirical evidence that
morphological variability in DMN regions
is linked to the reward circuitry (Fig. 2).
Finally, we detail how our process model relates
to previous accounts of DMN function and
we derive explicit hypotheses to be tested in future neuroscience
experiments (Box 1).

@@

\begin{figure}[!h]
  \includegraphics[width=1\linewidth]{VennDiagram-2017-09-08.pdf}
  \caption{\textbf{Situating Markov Decision Processes among other accounts of default mode function}
  This Venn diagram summarizes the relationship between four existing explanations of the functional role of the DMN and our present account. Viewing empirical findings in the DMN from the MDP viewpoint incorporates important aspects of the free energy principle, predictive coding, sentinal hypothesis, and semantic hypothesis.
  % more related to "What" DMN does. Our account of DMN by Markov Decision Process is at the intersection of those accounts and thus corresponds to a "Process model" meaning a model of both "How" and "What" a process occur.
  The MDP account may reconcile several strengths of these functional accounts in a process model that simultaneously acknowledges environmental input and behavioral choices as well as the computational and algorithmic properties (How? and What?) underlying higher-order control of the organism.

  % ; here the mental processes and how it relate to observed behavior. For each account, 4 icons describe the core concepts of Time horizon, Neural plasticity, Hierarchy, and Behavioral goal. The "Time horizon" should be understood as a weighting of the expected future outcomes shorter to longer terms into present decision making. Then, "online monitoring" of the environment means detecting and processing salient cues in the sensory environment. The "Predictive Coding" is understood here as the joint minimization of feedforward prediction error and feedback modulation to optimize neural processing; there is thus no notion of an agent with behavioral goal.
  }
  \label{fig:VennDiagram}
\end{figure}
